---
title: "Cell Cycle plotting"
output: html_notebook
---

#Set working directory to appropriate folder for inputs and outputs on Google Drive
```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for aria's computer
#knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/.shortcut-targets-by-id/1zSqx3IzXMwt6clUjwyqmlOf4G1K53lvy/Fasse_Shared/AJF_Drive_copy/Experiments/AJF009') # for dylan's computer

#2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/ is additional path for outputs

```

#Initialize
```{r include = FALSE}
rm(list = ls())
library(dplyr)
library(Seurat)
library(ggplot2)
library(RColorBrewer)

`%nin%` = Negate(`%in%`)
```

# Load data
```{r}
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/all_data_final_lineages.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Preprocess_GEX/second_timepoint_merged.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Filtering_cDNA/resistant_lineage_lists.RData')

load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/cis_final_lineages.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/cocl2_final_lineages.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/dabtram_final_lineages.RData')
load('2022_01_14_analysis_scripts/2022_05_27_analysis/Assign_dominant_barcodes/dabtram_both_times_final_lineages.RData')

```

#Plot cell cycle
```{r}

# view cell cycle scores and phase assignments
DimPlot(all_data, group.by = "Phase")
DimPlot(all_data)
FeaturePlot(object = all_data, reduction = 'umap', features = ("nFeature_RNA"), pt.size = 1, combine = T, order = TRUE)
DimPlot(all_data, group.by = "OG_condition", cols = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29', 'dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C'))

```

# Markers within each first drug object to find subgroups (ie analogous to NGFR/EGFR)
```{r}
#load('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/all_data_markers.RData')
cis_markers <- FindAllMarkers(cis, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
cocl2_markers <- FindAllMarkers(cocl2, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
dabtram_markers <- FindAllMarkers(dabtram, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)

all_data.markers <- FindAllMarkers(all_data, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25) 
save(all_data.markers, cis_markers, cocl2_markers, dabtram_markers, file = 'all_data_markers.RData')
```

# need to make Idents metadata object which says if the cells are included in the combined lins list, or if they were filtered
```{r}

fivecell_cDNA$DabTramMaintained <- Reduce(intersect, list(fivecell_cDNA$DabTram, fivecell_cDNA$DabTramtoDabTram))

filtered_meta <- rep(0, length(names(all_data$Lineage)))

filtered_meta[which(all_data$OG_condition == "dabtram" & all_data$Lineage %in% combined_lins_list$DabTram)] <- 'Resistant to DabTram'
filtered_meta[which(all_data$OG_condition == "dabtramtodabtram" & all_data$Lineage %in% combined_lins_list$DabTramtoDabTram)] <- 'Resistant to DabTramtoDabTram'
filtered_meta[which(all_data$OG_condition == "dabtramtococl2" & all_data$Lineage %in% combined_lins_list$DabTramtoCoCl2)] <- 'Resistant to DabTramtoCoCl2'
filtered_meta[which(all_data$OG_condition == "dabtramtocis" & all_data$Lineage %in% combined_lins_list$DabTramtoCis)] <- 'Resistant to DabTramtoCis'
filtered_meta[which(all_data$OG_condition == "cocl2" & all_data$Lineage %in% combined_lins_list$CoCl2)] <- 'Resistant to CoCl2'
filtered_meta[which(all_data$OG_condition == "cocl2todabtram" & all_data$Lineage %in% combined_lins_list$CoCl2toDabTram)] <- 'Resistant to CoCl2toDabTram'
filtered_meta[which(all_data$OG_condition == "cocl2tococl2" & all_data$Lineage %in% combined_lins_list$CoCl2toCoCl2)] <- 'Resistant to CoCl2toCoCl2'
filtered_meta[which(all_data$OG_condition == "cocl2tocis" & all_data$Lineage %in% combined_lins_list$CoCl2toCis)] <- 'Resistant to CoCl2toCis'
filtered_meta[which(all_data$OG_condition == "cis" & all_data$Lineage %in% combined_lins_list$Cis)] <- 'Resistant to Cis'
filtered_meta[which(all_data$OG_condition == "cistodabtram" & all_data$Lineage %in% combined_lins_list$CistoDabTram)] <- 'Resistant to CistoDabTram'
filtered_meta[which(all_data$OG_condition == "cistococl2" & all_data$Lineage %in% combined_lins_list$CistoCoCl2)] <- 'Resistant to CistoCoCl2'
filtered_meta[which(all_data$OG_condition == "cistocis" & all_data$Lineage %in% combined_lins_list$CistoCis)] <- 'Resistant to CistoCis'

filtered_meta[which(all_data$OG_condition == "dabtram" & all_data$Lineage %in% fivecell_cDNA$DabTram)] <- 'Large Resistant to DabTram'
filtered_meta[which(all_data$OG_condition == "dabtramtodabtram" & all_data$Lineage %in% fivecell_cDNA$DabTramtoDabTram)] <- 'Large Resistant to DabTramtoDabTram'
filtered_meta[which(all_data$OG_condition == "dabtramtococl2" & all_data$Lineage %in% fivecell_cDNA$DabTramtoCoCl2)] <- 'Large Resistant to DabTramtoCoCl2'
filtered_meta[which(all_data$OG_condition == "dabtramtocis" & all_data$Lineage %in% fivecell_cDNA$DabTramtoCis)] <- 'Large Resistant to DabTramtoCis'
filtered_meta[which(all_data$OG_condition == "cocl2" & all_data$Lineage %in% fivecell_cDNA$CoCl2)] <- 'Large Resistant to CoCl2'
filtered_meta[which(all_data$OG_condition == "cocl2todabtram" & all_data$Lineage %in% fivecell_cDNA$CoCl2toDabTram)] <- 'Large Resistant to CoCl2toDabTram'
filtered_meta[which(all_data$OG_condition == "cocl2tococl2" & all_data$Lineage %in% fivecell_cDNA$CoCl2toCoCl2)] <- 'Large Resistant to CoCl2toCoCl2'
filtered_meta[which(all_data$OG_condition == "cocl2tocis" & all_data$Lineage %in% fivecell_cDNA$CoCl2toCis)] <- 'Large Resistant to CoCl2toCis'
filtered_meta[which(all_data$OG_condition == "cis" & all_data$Lineage %in% fivecell_cDNA$Cis)] <- 'Large Resistant to Cis'
filtered_meta[which(all_data$OG_condition == "cistodabtram" & all_data$Lineage %in% fivecell_cDNA$CistoDabTram)] <- 'Large Resistant to CistoDabTram'
filtered_meta[which(all_data$OG_condition == "cistococl2" & all_data$Lineage %in% fivecell_cDNA$CistoCoCl2)] <- 'Large Resistant to CistoCoCl2'
filtered_meta[which(all_data$OG_condition == "cistocis" & all_data$Lineage %in% fivecell_cDNA$CistoCis)] <- 'Large Resistant to CistoCis'

filtered_meta[which(all_data$OG_condition == "dabtram" & all_data$Lineage %in% fivecell_cDNA$DabTramMaintained)] <- 'Maintained Resistant to DabTram'
filtered_meta[which(all_data$OG_condition == "dabtramtodabtram" & all_data$Lineage %in% fivecell_cDNA$DabTramMaintained)] <- 'Maintained Resistant to DabTramtoDabTram'

filtered_meta[which(all_data$OG_condition == "dabtram" & all_data$Lineage %nin% combined_lins_list$DabTram & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "dabtramtodabtram" & all_data$Lineage %nin% combined_lins_list$DabTramtoDabTram & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "dabtramtococl2" & all_data$Lineage %nin% combined_lins_list$DabTramtoCoCl2 & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "dabtramtocis" & all_data$Lineage %nin% combined_lins_list$DabTramtoCis & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cocl2" & all_data$Lineage %nin% combined_lins_list$CoCl2 & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cocl2todabtram" & all_data$Lineage %nin% combined_lins_list$CoCl2toDabTram & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cocl2tococl2" & all_data$Lineage %nin% combined_lins_list$CoCl2toCoCl2 & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cocl2tocis" & all_data$Lineage %nin% combined_lins_list$CoCl2toCis & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cis" & all_data$Lineage %nin% combined_lins_list$Cis & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cistodabtram" & all_data$Lineage %nin% combined_lins_list$CistoDabTram & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cistococl2" & all_data$Lineage %nin% combined_lins_list$CistoCoCl2 & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 
filtered_meta[which(all_data$OG_condition == "cistocis" & all_data$Lineage %nin% combined_lins_list$CistoCis & all_data$Lineage %nin% c("No Barcode", "Still multiple"))] <- 'Filtered out' 

filtered_meta[which(all_data$Lineage %in% c("No Barcode", "Still multiple"))] <- 'No Barcode'

print(table(filtered_meta))

```

```{r}
all_data$Resistant_filtered <- filtered_meta
Idents(all_data) <- all_data$Resistant_filtered
```

```{r}
pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/test_plot.pdf', height = 10, width = 20)
DimPlot(all_data, group.by = 'ident', cols = )
DimPlot(all_data, group.by = "Lineage") + theme(legend.position = 'none')
dev.off()

```

```{r}
pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/test_violin.pdf', height = 10, width = 30)

VlnPlot(all_data, features = 'NGFR', idents = 'Maintained Resistant to DabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'EGFR', idents = 'Maintained Resistant to DabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'NGFR', idents = 'Maintained Resistant to DabTramtoDabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'EGFR', idents = 'Maintained Resistant to DabTramtoDabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)

VlnPlot(all_data, features = 'NGFR', idents = 'Large Resistant to DabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'EGFR', idents = 'Large Resistant to DabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'NGFR', idents = 'Large Resistant to DabTramtoDabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)
VlnPlot(all_data, features = 'EGFR', idents = 'Large Resistant to DabTramtoDabTram', group.by = "Lineage") + theme(legend.position = 'none') + geom_boxplot(fill = 'white', width = 0.1)

dev.off()
#VlnPlot(all_data, features = 'NGFR', idents = all_data$OG_condition == 'dabtram', group.by = "lineage")
```

#Looking into the one lineage that switches ngfr -> egfr
```{r}

switch_lin <- names(all_data$orig.ident[all_data$Lineage == "Lin171516"])
DimPlot(all_data, group.by = "OG_condition", cols = c('dabtram' = '#623594', 'cocl2' = '#0F8241', 'cis' = '#C96D29', 'dabtramtodabtram' = '#561E59', 'dabtramtococl2' = '#A2248E', 'dabtramtocis' = '#9D85BE', 'cocl2todabtram' = '#10413B', 'cocl2tococl2' = '#6ABD45', 'cocl2tocis' = '#6DC49C', 'cistodabtram' = '#A23622', 'cistococl2' = '#F49129', 'cistocis' = '#FBD08C'))
DimPlot(all_data, cells.highlight = list(switch_lin))

switch_lin <- names(dabtram$orig.ident[dabtram$Lineage == "Lin171516"])
DimPlot(dabtram)
DimPlot(dabtram, cells.highlight = list(switch_lin))

#need to integrate lineages into just dabtram object and then plot off of this isntead?
#vlnplot(all_data, features = ngfr, idents = just the cells resistant to dabtram, group.by = lineage but i only want those included in combined_lins_list$dabtram ?

```

#from dabtram_both_times, force 2 clusters in umap, plot vs ngfr egfr, find markers of these 2
```{r}

dabtram_both_times_markers <- FindAllMarkers(dabtram_both_times, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
DimPlot(dabtram_both_times)
DimPlot(dabtram_both_times, group.by = 'OG_condition')
FeaturePlot(dabtram_both_times, features = c('NGFR', 'EGFR', 'nFeature_RNA'))
```

#Assign cluster assignments per lineage, find average score per lineage
```{r}
#average cell assignments per lineage in dabtram_maintained

#want to do a stacked barplot here-- copy paste code from condition clustering

#get lineage and cluster data from seurat object, switch cluster identifiers from 0,1 to -1,1 (egfr, ngfr)
clusters_per_lin <- data.frame (Cluster = as.numeric(as.character(dabtram_both_times$seurat_clusters)), Lineage = dabtram_both_times$Lineage, condition = dabtram_both_times$OG_condition)
clusters_per_lin$Cluster[clusters_per_lin$Cluster == 0] <- -1
clusters_per_lin_list <- list()


pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/clusters_per_lin_dabtram.pdf')
for (i in fivecell_cDNA$DabTramMaintained){
  currentlin <- filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtram')
  clusters_per_lin_list[[i]] <- data.frame(table(currentlin$Cluster))
  clusters_per_lin_list[[i]]$Score <- weighted.mean(as.numeric(as.character(clusters_per_lin_list[[i]]$Var1)), clusters_per_lin_list[[i]]$Freq)
  print(ggplot(clusters_per_lin_list[[i]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(position = 'fill', stat = 'identity') 
        + labs(title = paste('cluster of cells in lineage', i, 'num cells', sum(clusters_per_lin_list[[i]]$Freq), 'score', clusters_per_lin_list[[i]]$Score[1])) 
        + scale_fill_manual(values = c('-1' = 'white', '1' = 'black')))
}
dev.off()

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/clusters_per_lin_dabtramtodabtram.pdf')
for (i in fivecell_cDNA$DabTramMaintained){
  currentlin <- filter(clusters_per_lin, clusters_per_lin$Lineage == i & clusters_per_lin$condition == 'dabtramtodabtram')
  clusters_per_lin_list[[paste(i, 'second')]] <- data.frame(table(currentlin$Cluster))
  clusters_per_lin_list[[paste(i, 'second')]]$Score <- weighted.mean(as.numeric(as.character(clusters_per_lin_list[[paste(i, 'second')]]$Var1)), clusters_per_lin_list[[paste(i, 'second')]]$Freq)
  print(ggplot(clusters_per_lin_list[[paste(i, 'second')]], aes(x ='', y = Freq, fill = Var1)) + geom_bar(position = 'fill', stat = 'identity') 
        + labs(title = paste('cluster of cells in lineage', i, 'num cells', sum(clusters_per_lin_list[[paste(i, 'second')]]$Freq), 'score', clusters_per_lin_list[[paste(i, 'second')]]$Score[1])) 
        + scale_fill_manual(values = c('-1' = 'white', '1' = 'black')))
}
dev.off()
```

#Plot scores as heatmap
```{r}
score_matrix <- matrix(ncol = 2, nrow = length(fivecell_cDNA$DabTramMaintained))
colnames(score_matrix) <- c('time 1', 'time 2')
rownames(score_matrix) <- unlist(fivecell_cDNA$DabTramMaintained)

for (i in rownames(score_matrix)){
  score_matrix[i, 'time 1'] <- clusters_per_lin_list[[i]]$Score[1]
  score_matrix[i, 'time 2'] <- clusters_per_lin_list[[paste(i, 'second')]]$Score[1]
}

score_matrix <- score_matrix[order(score_matrix[,1], decreasing = TRUE),]

pdf('2022_01_14_analysis_scripts/2022_05_27_analysis/Lineage_expression/heatmap_test.pdf', width = 10, height = 12)
heatmap(score_matrix, scale = "none", Colv = NA, Rowv = NA, col = brewer.pal(n = 9, name = 'Greys'))
dev.off()

```
